---
title: "longBarsPANative.R Execution Report"
output:
  pdf_document:
    highlight: zenburn
classoption: landscape
geometry: margin=0.25in
---
## Input Parameters
Program Name: longBarsPANative.R   
Ticker: `r ticker`   
Start Date: `r startDate`    
End Date:  `r endDate`   
Bar Size: `r barSizeInMins` Minutes   
SMA Length:  48 Bars   

## Group Trade Statistics

```{r echo=TRUE, tidy=TRUE, message=FALSE, results='asis'}
print(xtable(tableTradeStats,
             digits=c(0,0,2,0,2,0,2),
             caption=paste("Trade Statistics 1 ---", subsetStr),
             label="Trade Stats 1"
            ), 
      include.rownames=FALSE, include.colnames=FALSE, caption.placement="top", 
      size="normalsize",
      type="latex",
      comment=FALSE
      )
```


``` {r echo=TRUE, tidy=TRUE, message=FALSE, results='asis'}
print(xtable(tablePerformanceStats, 
             digits=c(0,0,3,0,3),
             caption=paste("Performance Statistics 2 --- ", subsetStr),
             label="Performance Stats 2" 
            ), 
      include.rownames=FALSE, include.colnames=FALSE, caption.placement="top", 
      size="normalsize",
      type="latex",
      comment=FALSE
      )
```


<!---
##    Cannot use chart.Posn in RMarkdown, which is too bad.  The following
##    error is produced:  (it's a bounding box error... nothing to do with
##    ghostscript - this is the error message as pdfcrop prints it).
##
##    cropping /Users/stergios/tmp/report-SPY_files/figure-latex/unnamed-chunk-11.pdf
##    PDFCROP 1.38, 2012/11/02 - Copyright (c) 2002-2012 by Heiko Oberdiek.
##    !!! Error: Ghostscript does not report bounding boxes!
##    ``` {r echo=TRUE}
##    chart.Posn(Portfolio=strategyStr, Symbol=tickerSymbol)
##    ```
-->

\newpage

## MAE/MFE graphs

Use the data from a backtest or production trade to evaluate where stop loss or
profit taking orders could be added.

### MFE
* trades on the diagonal axis closed on their highs
* trades on the vertical axis experienced no positive P&L
* the horizontal line demonstrates the influence of a stop in this data set

``` {r echo=FALSE, tidy=TRUE, message=FALSE, results='asis', fig.width=10, fig.height=7.5}
chart.ME(strategyStr, Symbol=tickerSymbol, type="MFE")
```

\newpage

### MAE
* trades on diagonal axis closed on their lows
* trades on vertical axis experienced no drawdown

``` {r echo=FALSE, tidy=TRUE, message=FALSE, results='asis', fig.width=10, fig.height=7.5}
chart.ME(strategyStr, Symbol=tickerSymbol, type="MAE")
```

\newpage

## Performance Summary

``` {r echo=FALSE, tidy=TRUE, message=FALSE, results='asis', fig.width=10, fig.height=7.5}
charts.PerformanceSummary(rets, colorset=bluefocus, main=paste(ticker, strategyStr, "Performance") )
```
<!---
##    The above function combines the follow charts on to one page:
##    chart.CumReturns(R=rets, colorset=bluefocus, main=paste(ticker, strategyStr, "Cumulative Returns") )
##    chart.BarVaR(R=rets, colorset=bluefocus, main=paste(ticker, strategyStr, "Periodic Returns") )
##    chart.TimeSeries(R=rets, colorset=bluefocus, main=paste(ticker, strategyStr, "Drawdown") )
-->

## Full Graph

``` {r echo=FALSE, tidy=TRUE, message=FALSE, results='asis', fig.width=10, fig.height=7.5}
messageStr = paste( ticker, "-", barSizeInMins, "min", sep="")
epSS   = ep
explSS = expl
tpSS   = tp
chartSeries(OHLCV(S), 
            name=messageStr,
            type="candlesticks",
            theme=chartTheme(theme='white', up.col='green', dn.col='red'),
            TA=taEnhanced
)
```

## Weekly Graphs

``` {r echo=FALSE, tidy=TRUE, message=FALSE, results='asis', fig.width=10, fig.height=7.5}
for(i in 1:length(allWeeksSS) ) {
  epSS   = ep[allWeeksSS[i]]
  explSS = expl[allWeeksSS[i]]
  tpSS   = tp[allWeeksSS[i]]

  chartSeries(OHLCV(S), 
              subset=allWeeksSS[i],
              name=messageStr,
              type="candlesticks",
              theme=chartTheme(theme='white', up.col='green', dn.col='red'),
              TA=taEnhanced
  )
}
```

\newpage

## Chart Histogram
<!--- Note: chart.Histogram has a bad habit of failing if there is only one trade in ptstats.  -->

``` {r echo=FALSE, tidy=TRUE, message=FALSE, results='asis', fig.width=10, fig.height=7.5}
if(nrow(ptstats)>1) {
  chart.Histogram(ptstats$Pct.Net.Trading.PL, methods=c('add.normal'), main='SMA48w2Away returns')
} else {
  PerformanceAnalytics:::textplot("There was only 1 trade (or maybe none at all???).  No sense in showing a histogram!", cex=0.75)
}
```

\newpage

## Trade Quantiles

``` {r echo=FALSE, tidy=TRUE, message=FALSE, results='asis'}
print(xtable(tradeQuantiles(Portfolio=strategyStr, Symbol=tickerSymbol, scale='percent', probs=c(.5,.9,.99)),
             digits=3,
             caption=paste("Trade Quantiles --- ", subsetStr),
             label="Trade Quantiles" 
            ), 
      include.rownames=TRUE, include.colnames=TRUE, caption.placement="top", 
      type="latex",
      comment=FALSE
      )
```

\newpage

## Net Trade Statistics
``` {r echo=FALSE, tidy=TRUE, message=FALSE, results='asis' }
t2=data.frame(
  a=names(tstats)[1:15],  b=as.numeric(tstats[1,1:15]),
  c=names(tstats)[16:30], d=as.numeric(tstats[1,16:30])
)
PerformanceAnalytics:::textplot(t2, show.rownames=FALSE, show.colnames=FALSE, cex=1.00)
```

\newpage

## Per Trade Statistics

<!---
Other font sizes to try can be found here:
https://en.wikibooks.org/wiki/LaTeX/Fonts#Sizing_text
size          -  standard classes, proc        - AMS classes, memoir            -  slides                 beamer
              -  [10pt]  - [11pt]   - [12pt]   - [10pt]   - [11pt]   - [12pt]   -          - [10pt]   - [11pt]   - [12pt]
\tiny         - 6.80565  - 7.33325  - 7.33325  - 7.33325  - 7.97224  - 8.50012  - 17.27505 - 5.31258  - 6.37509  - 6.37509
\scriptsize   - 7.97224  - 8.50012  - 8.50012  - 7.97224  - 8.50012  - 9.24994  - 20.73755 - 7.43760  - 8.50012  - 8.50012
\footnotesize - 8.50012  - 9.24994  - 10.00002 - 8.50012  - 9.24994  - 10.00002 - 20.73755 - 8.50012  - 9.24994  - 10.00002
\small        - 9.24994  - 10.00002 - 10.95003 - 9.24994  - 10.00002 - 10.95003 - 20.73755 - 9.24994  - 10.00002 - 10.95003
\normalsize   - 10.00002 - 10.95003 - 11.74988 - 10.00002 - 10.95003 - 11.74988 - 24.88382 - 10.00002 - 10.95003 - 11.74988
\large        - 11.74988 - 11.74988 - 14.09984 - 10.95003 - 11.74988 - 14.09984 - 29.86258 - 11.74988 - 11.74988 - 14.09984
\Large        - 14.09984 - 14.09984 - 15.84985 - 11.74988 - 14.09984 - 15.84985 - 35.82510 - 14.09984 - 14.09984 - 16.24988
\LARGE        - 15.84985 - 15.84985 - 19.02350 - 14.09984 - 15.84985 - 19.02350 - 43.00012 - 16.24988 - 16.24988 - 19.50362
\huge         - 19.02350 - 19.02350 - 22.82086 - 15.84985 - 19.02350 - 22.82086 - 51.60014 - 19.50362 - 19.50362 - 23.39682
\Huge         - 22.82086 - 22.82086 - 22.82086 - 19.02350 - 22.82086 - 22.82086 - 51.60014 - 23.39682 - 23.39682 - 23.39682
-->

``` {r echo=FALSE, tidy=TRUE, message=FALSE, results='asis'}
print(xtable(ptstatsStr[,perTradeStats1], 
             digits=3,
             caption=paste("Flat to Flat Per-Trade Statistics 1 --- ", subsetStr),
             label="Flat to Flat Per-Trade Statistics 1" 
            ), 
      include.rownames=FALSE, include.colnames=TRUE, caption.placement="top", 
      type="latex",
      size="large",
      comment=FALSE
      )
print(xtable(ptstatsStr[,perTradeStats2], 
             digits=3,
             caption=paste("Flat to Flat Per-Trade Statistics 2 --- ", subsetStr),
             label="Flat to Flat Per-Trade Statistics 2" 
            ), 
      include.rownames=FALSE, include.colnames=TRUE, caption.placement="top", 
      type="latex",
      size="large",
      comment=FALSE
      )
print(xtable(ptstatsStr[,perTradeStats3], 
             digits=3,
             caption=paste("Flat to Flat Per-Trade Statistics 3 --- ", subsetStr),
             label="Flat to Flat Per-Trade Statistics 3" 
            ), 
      include.rownames=FALSE, include.colnames=TRUE, caption.placement="top", 
      type="latex",
      size="large",
      comment=FALSE
      )
```

\newpage

## Transactions
``` {r echo=FALSE, tidy=TRUE, message=FALSE, results='asis' }
print(xtable(as.data.frame(transactions),
             caption="Transactions",
             label="Transactions"
            ), 
      floating=FALSE,
      include.rownames=TRUE, include.colnames=TRUE, caption.placement="top", 
      type="latex",
      size="large",
      comment=FALSE
      )
```

\newpage

## Order Book
<!---
I wish I could make long tables span multiple pages.  One of the
following should work, but neither does.

      tabular.environment='longtable'
      tabular.environment='tabu'

It produces the following error: 

! LaTeX Error: Environment longtable undefined.

Which seems like it would be simple to fix by installing the longtable
package.  But I've wasted enough time this morning trying to do so.

output file: reportNative.knit.md

/usr/local/bin/pandoc reportNative.utf8.md 
    --to latex 
    --from markdown+autolink_bare_uris+ascii_identifiers+tex_math_single_backslash-implicit_figures 
    --output ~/tmp/reportNative-SPY.pdf 
    --template /Library/Frameworks/R.framework/Versions/3.1/Resources/library/rmarkdown/rmd/latex/default.tex 
    --highlight-style zenburn 
    --latex-engine pdflatex 


! LaTeX Error: Environment longtable undefined.

References to help with installing this problem later on:

https://en.wikibooks.org/wiki/LaTeX/Tables

https://en.wikibooks.org/wiki/LaTeX/Installing_Extra_Packages#Manual_installation

      ( floating=FALSE, # should be false when using longtable. )

-->

``` {r echo=FALSE, tidy=TRUE, message=FALSE, results='asis' }
numberOBRows = nrow(obookDF)
rowsPerPage  = 30
startRows    = seq(1, numberOBRows, rowsPerPage)
endRows      = startRows+rowsPerPage
endRows[length(endRows)] = numberOBRows

for(i in 1:length(startRows) ) {
  print(xtable(obookDF[startRows[i]:startRows[i]:endRows[i], ],
               caption="Order Book",
               label="Order Book"
              ), 
        floating=FALSE,
        include.rownames=TRUE, include.colnames=TRUE, caption.placement="top", 
        type="latex",
        size="large",
        comment=FALSE
        )
}
```
